---
title: "Fraud Detection"
output: github_document
---

Read the dataset
```{r}
#fraud_data = read.csv("Fraud.csv")

```
Check for NA or null
```{r}

anyNA(fraud_data)
```
Data set has no Null or NA 



Let see the nature of the data
```{r}
summary(fraud_data)
```

From the above, the Features are:

1) Step Represent the hour the transaction.
2) Type of the transaction Cash_In,Cash_Out, DEBIT, PAYMENT, TRANSFER.
3) A Mount money transferred.
4) nameOrgin is Sender info
5) Oldbalanceorg is the balance before sending 
6) NewbalnceOrgin is the balance after sending
7) name Destination is the receiver info.
8) oldbalancdest is the balance before receiving the money.
9) Oldbalancdest is the balance after the amount received,
10) isFraud is the transaction is corrupted or Proper valid Transaction (0 or 1).



visualize Data.



Let see what the ratio of fraud vs valid transaction
```{r}
print(nrow(fraud_data[fraud_data$isFraud == 0,]))
print(nrow(fraud_data[fraud_data$isFraud == 1,]))
```

lets see all the transaction with the fraud transaction for each Type of Transaction.

```{r}
print(nrow( fraud_data[fraud_data$type == "CASH_IN" & fraud_data$isFraud == 1,]))

print(nrow( fraud_data[fraud_data$type ==  "CASH_OUT" & fraud_data$isFraud == 1,]))
print(nrow( fraud_data[fraud_data$type ==  "DEBIT" & fraud_data$isFraud == 1,]))
print(nrow( fraud_data[fraud_data$type ==  "PAYMENT" & fraud_data$isFraud == 1,]))
print(nrow( fraud_data[fraud_data$type ==  "TRANSFER" & fraud_data$isFraud == 1,]))
```

```{r}
library(ggplot2)

ggplot(fraud_data, aes( x = type, y = isFraud ,color = type )) + geom_point() + theme_classic()
```


From the above we can see both the CASH_OUT and Transfer Alone have Fradulent. and both have equal amount of transaction 4116 and 4097  

Let see the Transaction where max and min of Fraud transaction



```{r}
library(ggplot2)

ggplot(fraud_data, aes(x = type ) ) + geom_bar(aes(fill =isFraud)) + theme_bw()
```





























